Proof equivalence in \capsabbrev{mll} is \capsabbrev{pspace}-complete

### 2015-10-16 main/LMCS.tex
Use “3-partition” rather than “3-Partition” consistently

Both Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994} use a reduction from (a variant of) the 3-Partition problem to show  \capsabbrev{np}-hardness. Such reductions provide a good illustration of how the linearity of \capsabbrev{mll} can be used to encode combinatoric problems. In this section we will discuss a similar reduction from 3-Partition.

@@

An instance of the 3-Partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$. The decision problem asks whether a partitioning exists of $I$ into $n$ triples $(i_a,i_b,i_c)$ each with sum $k$. It may be assumed that each $i\in I$ lies between $\nicefrac k4$ and $\nicefrac k2$, so that any partitioning into \emph{subsets} with sum $k$ is a solution, since each subset of sum $k$ necessarily has $3$ elements. The 3-Partition problem is strongly \capsabbrev{np}-complete \cite{GareyAndJohnson}, which means it remains \capsabbrev{np}-complete with a unary encoding of the values in $I$.

We will give a simple encoding of 3-partition in MLL proof search, similar to those of Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994}. A 3-Partition instance $I$ is encoded by a sequent consisting of:
\begin{itemize}
	\item a formula $\bigtn(\bot^{i+1})$ for each $i\in I$, and
	\item the formula $\bigtn(K^n)$ where $K=\bigparr(\1^{k+1})$.
\end{itemize}
A solution to the 3-partition problem is encoded as a proof net as follows. If the numbers $a$, $b$, and $c$ are assigned to a triple corresponding to a formula $K_j$, then the corresponding formulae have $a+1$, $b+1$, and $c+1$ occurrences of $\bot$, and $k+1=a+b+c+1$ occurrences of $\1$, respectively. Then as described previously, there is a proof net for these formulae, obtained by attaching each jump to a distinct $\1$, with the exception of three jumps, one each from $a$, $b$, and $c$, overlapping on exactly one instance.

>>>>

Both Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994} use a reduction from (a variant of) the 3-partition problem to show  \capsabbrev{np}-hardness. Such reductions provide a good illustration of how the linearity of \capsabbrev{mll} can be used to encode combinatoric problems. In this section we will discuss a similar reduction from 3-partition.

@@

An instance of the 3-partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$. The decision problem asks whether a partitioning exists of $I$ into $n$ triples $(i_a,i_b,i_c)$ each with sum $k$. It may be assumed that each $i\in I$ lies between $\nicefrac k4$ and $\nicefrac k2$, so that any partitioning into \emph{subsets} with sum $k$ is a solution, since each subset of sum $k$ necessarily has $3$ elements. The 3-partition problem is strongly \capsabbrev{np}-complete \cite{GareyAndJohnson}, which means it remains \capsabbrev{np}-complete with a unary encoding of the values in $I$.

We will give a simple encoding of 3-partition in MLL proof search, similar to those of Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994}. A 3-partition instance $I$ is encoded by a sequent consisting of:
\begin{itemize}
	\item a formula $\bigtn(\bot^{i+1})$ for each $i\in I$, and
	\item the formula $\bigtn(K^n)$ where $K=\bigparr(\1^{k+1})$.
\end{itemize}
A solution to the 3-partition problem is encoded as a proof net as follows. If the numbers $a$, $b$, and $c$ are assigned to a triple corresponding to a formula $K_j$, then the corresponding formulae have $a+1$, $b+1$, and $c+1$ occurrences of $\bot$, and $k+1=a+b+c+1$ occurrences of $\1$, respectively. Then as described previously, there is a proof net for these formulae, obtained by attaching each jump to a distinct $\1$, with the exception of three jumps, one each from $a$, $b$, and $c$, overlapping on exactly one instance.
